%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Chinavat Nachaithong
\documentclass[margin,line]{resume}

\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs} % Added for professional, tight table spacing

\title{Resume_Chinavat Nachaithong}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\LARGE Chinavat Nachaithong}
\begin{resume}

    %__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
    \section{\mysidestyle \textbf{Contact Information}}

    Applied Computer Science Student \hfill E-mail: \texttt{\href{mailto:monshinawatra@gmail.com}{monshinawatra@gmail.com}} \\
    King Mongkut's University of Technology Thonburi (KMUTT) \hfill Mobile: \texttt{061-449-3292} \\
    Bangkok, Thailand \hfill GitHub / LinkedIn: \texttt{monshinawatra} \\
    
    \vspace{-4mm}       
    \section{\mysidestyle \textbf{Education}} 
    \vspace{-2mm}
    
    \noindent
    \begin{tabular}{@{} p{2cm} p{5cm} p{4.8cm} p{2.4cm} @{}}
    \toprule
    \textbf{Year} & \textbf{Degree} & \textbf{Institute/School} & \textbf{Details} \\ 
    \midrule
    \textbf{2022-2026} & B.Sc., Applied Computer Science & King Mongkut's University of Technology Thonburi & GPAX: 3.69 \\
                      &                                 &                                                  & Scholarship$\ddagger$ \\ 
    \bottomrule
    \end{tabular}
    \vspace{-3mm}
    
    \textsuperscript{$\ddagger$} Petchra Pra Jom Klao Scholarship --- maintaining a GPAX $\geq$ 3.40.
    \vspace{-3mm}
    \section{\mysidestyle \textbf{Awards \&\\Highlights}}
    \begin{list2}
    \item \textbf{SuperAI Engineer Season 4 --- Gold Medalist}: National Top 10 finisher (one of only 10 awarded); won 50,000 THB at the AI Thailand Forum 2024.
    \item \textbf{Typhoon Hackathon 2024 --- Finalist}: Built LawBuddy, a fine-tuned Thai legal LLM paired with a custom RAG pipeline.
    \item \textbf{Academic Publication}: Research on Google Play review-quality scoring with Transformer models; accepted and presented at iSAI-NLP 2025.
    \end{list2}
    \vspace{-3mm}

    %__________________________________________________________________________________________________________________
    % AI & Game Design Projects
    \section{\mysidestyle \textbf{AI $\times$ Game\\Design\\Projects}}
     
    \underline{\textbf{NeuroGami --- Creature-Battler with Reinforcement Learning Core Loop}} \hfill \textit{(2026)} \vspace{0.3mm}
    \begin{list2}
    \item Developed a framework where monsters have no scripted moves; each carries its own learning agent that gets smarter from every fight.
    \item Designed the state, action, reward mechanics, and battle pacing so the learning stays legible, balanced, and fun. 
    \item KMUTT final-year project, currently in active development as a live-service title.
    \end{list2}
    \vspace{-3mm}

    \underline{\textbf{MADX --- Multiplayer AI Diffusion eXperience}} \hfill \textit{(2025)} \vspace{0.3mm}
    \begin{list2}
    \item Designed a two-player game whose world structure is the neural network itself.
    \item Utilized an open-source diffusion world-model to render each frame dynamically based on both players' choices (ATARI Boxing).
    \end{list2}
    \vspace{-3mm}

    \underline{\textbf{Agnetic --- Solo Magnet-Polarity Puzzle Game}} \hfill \textit{(2021)} \vspace{0.3mm}
    \begin{list2}
    \item Shipped a complete, rule-driven puzzle game in 48 hours and released it on itch.io during the GMTK Game Jam 2021.
    \item Iterated solo for 5 months post-jam tuning mechanical constraints, level logic, and difficulty curves.
    \end{list2}
    \vspace{-3mm}

    \underline{\textbf{Dungeon Delivery --- Top-Down Action Game}} \hfill \textit{(2023)} \vspace{0.3mm}
    \begin{list2}
    \item Designed an inverted-progression hook where the player starts unstoppable and grows weaker, forcing strategic resource management.
    \item Shipped with a small team in 48 hours for the Global Game Jam 2023 and released onto itch.io.
    \end{list2}
    \vspace{-3mm}

    \underline{\textbf{Gamify Habits Tracker --- Monster-Taming Habit App}} \hfill \textit{(2024)} \vspace{0.3mm}
    \begin{list2}
    \item Applied variable-reward, collection mechanics, and progression psychology to drive real-world consistency.
    \item Took the project seamlessly from an initial behavioral design concept to a working software application.
    \end{list2}
    \vspace{-3mm}

    % AI / ML Experience
    \section{\mysidestyle \textbf{AI / ML\\Experience}}

    \underline{\textbf{DeepCapital --- AI Engineer, Computer Vision}} \hfill \textit{(2024 -- 2026)} \vspace{0.3mm}
    \begin{list2}
    \item Shipped production computer vision models from prototype to deployment.
    \item Developed factory automation features (auto-counting, quality inspection) alongside multi-camera CCTV surveillance pipelines.
    \item Developed a multi-camera coordination pipeline featuring robust vehicle tracking and localized license plate recognition.
    \end{list2}
    \vspace{-3mm}
    
    \underline{\textbf{Looloo Technology --- Machine Learning Engineer}} \hfill \textit{(2021 -- 2023)} \vspace{0.3mm}
    \begin{list2}
    \item Led data pipeline development for the Universal Text Detector project.
    \item Executed QA and structured error-analysis workflows for Thai-English handwritten OCR pipelines.
    \end{list2}
    \vspace{-3mm}

    % Technical Skills
    \section{\mysidestyle \textbf{Technical\\Skills}} 
    
    \textbf{Game Design} - Core mechanics \& systems design, reward / progression loops, gamification design, player psychology, level design, rapid prototyping under jam constraints. \\
    \textbf{AI / ML} - Reinforcement learning (GRPO, reward shaping), LLM fine-tuning \& prompt engineering (Typhoon, OpenThai-GPT), diffusion world models, computer vision (YOLOv26, Grounded-SAM, TrOCR, SAM3, LLMdet). \\
    \textbf{Tools \& Stacks} - Python, PyTorch, Hugging Face, Flutter, Next.js, React, Git, Unity, Blender.
    \vspace{-3mm}

\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF